Soundness Proof of Dynamic Shortcut

### 2020-11-20 paper/pldi21/report/def.tex
Minor change in report

We could configure when the sealed symbolic execution or the abstract
interpretation is performed based on the definition of the converter
$\asconverter$.  For example, we could define the $\asconverter$ for analysis
elements related to only function entry, call, and exit points to perform
conversions in a function level.  For the soundness and the termination of the
the abstract interpretation with dynamic shortcuts, it should satisfy the
following condition:
\begin{theorem}\label{theorem:shortcut}
  The abstract interpretation with dynamic shortcut is sound and terminates in a
  finite time if its abstract semantics is sound and $\saconverter$ satisfies the
  following condition:
  \[
    \asconverter((\view, \abselem)) = (\absimap, \symbst) \Rightarrow
    \symbst \symbtrans^k \excst \wedge 1 < k \leq N
  \]
  where $N$ is a pre-defined maximum length of the sealed symbolic execution.
\end{theorem}

>>>>

We could configure when the sealed symbolic execution or the abstract
interpretation is performed based on the definition of the converter
$\asconverter$.  For example, we could define the $\asconverter$ for analysis
elements related to only function entry, call, and exit points to perform
conversions in a function level.  For the soundness and the termination of the
the abstract interpretation with dynamic shortcuts, it should satisfy the
following condition:
\begin{theorem}[Soundness and Termination]\label{theorem:shortcut}
  The abstract interpretation with dynamic shortcut is sound and terminates in a
  finite time if its abstract semantics is sound and $\saconverter$ satisfies the
  following condition:
  \begin{equation}\label{expr:condition}
    \asconverter((\view, \abselem)) = (\absimap, \symbst) \Rightarrow
    \symbst \symbtrans^k \excst \wedge 1 < k \leq N
  \end{equation}
  where $N$ is a pre-defined maximum length of the sealed symbolic execution.
\end{theorem}
